---
title: 'Predictive Analytics homework - Conjoint Analysis (Preferences for Mobile Communication Services)'
author: "Godfred Somua-Gyimah"
date: "January 10, 2017"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Note**: In order to run this demo, the following R packages must be installed in your R environment:

- ggplot2: visualization
- conjoint: marketing conjoint analysis

&nbsp;
&nbsp;

\newpage

# 1. Read in Dataset
```{r}
# Clean the environment
rm(list = ls())
# Read data file
df <- read.csv("mobile_services_ranking.csv")

```

# 2. Understand Data

```{r}
# Show head
head(df)

```
```{r}
# Show the structure of the data frame
str(df)

```

```{r}
# Show summary statistics
summary(df)

```

# 3. Exploratory Data Analysis

We can draw a couple of plots to explore the data.

First, load ggplot2 package.

```{r}
# Load ggplot2 package for plotting
library(ggplot2)
```

```{r}
# Draw box plot of ranking by brand 
ggplot(df,aes(x=brand, y=ranking, fill=brand)) +
  geom_boxplot()
```

```{r}
# Draw box plot of ranking by startup cost 
ggplot(df,aes(x=startup, y=ranking, fill=startup)) +
  geom_boxplot()
```

```{r}
# Draw box plot of ranking by monthly cost 
ggplot(df,aes(x=monthly, y=ranking, fill=monthly)) +
  geom_boxplot()
```

From the above box plot, we can see it clearly that ranking is higher with lower monthly cost.

# 4. Regression Analysis of the Main Effect Model
```{r}
# Fit linear regression model using main effects only (no interaction terms)
fit <- lm(ranking ~.,data= df)

print(summary(fit))

```

```{r}
# Show coefficient rounding to the nearest hundredth
formatC(fit$coefficients[-1], format = 'f', digits = 2)
```


# 5. Traditional Conjoint Analysis

```{r}
# Load the conjoint package
library(conjoint)

```

## 5.1. Prepare Data

```{r}
# Create levels
level = c(levels(df$brand),
          levels(df$startup),
          levels(df$monthly),
          levels(df$service),
          levels(df$retail),
          levels(df$apple),
          levels(df$samsung),
          levels(df$google))

# Remove double quote in the levels
level <- gsub('"','',level)

level
```

```{r}
# Create profiles
profiles <- df[1:8]

profiles
  
```

```{r}
# Create ratings of respondent
ratings = df[9]

head(ratings)
```

## 5.2. Calculate Attribute Importance

```{r}
# Calculate the importance of each attribute
im = caImportance(y=ratings, x=profiles)
names(im) = names(profiles)
im
```

```{r, fig.width= 8}
barplot(sort(im, decreasing = TRUE),col=1:length(im), main = "Attribute Importance")
```


## 5.3. Calculate Part Worths

```{r}
pw <- caUtilities(y=ratings, x=profiles, z=level)
```


```{r}
names(pw) = c('intercept',level)

# Show part worths rounding to the nearest hundredth
formatC(pw[-1], format = 'f', digits = 2)  # Do not show intercept
```


```{r}
# Show coefficient rounding to the nearest hundredth
formatC(fit$coefficients[-1], format = 'f', digits = 2)
```

Compare the above part worths and OLS coefficients, can you find out their relationship?

```{r, fig.width=10, fig.height=14}
#  Create a vector that assigns the same color value to levels under a same attribute
cols = c(1,1,1,1,2,2,2,2,3,3,3,3,4,4,5,5,6,6,7,7,8,8)

# Draw barplot of part worths  
bp <- barplot(pw[-1],las = 1, horiz = TRUE, xlim = c(-6, 7),axisnames = FALSE,
        col = cols, main = "Part Worths (Utilities)")

text(x= 5.8, y= bp, cex = 0.9,
     labels= paste(level,
                   "(",
                   formatC(pw[-1], format = 'f', digits = 2),
                   ')'))
# Add legend
legend(-6, 26,names(profiles), pch =0, cex = 1.5, fill = 1:8)

```




